---
title: "Rps10 metabarcoding primer ordering and mixing protocol"
output:
  html_document: default
  pdf_document:
    latex_engine: xelatex
mainfont: Arial
---

```{r setup, include=FALSE}
source("style.R")
```

*Updated October 2018*

The propose of the rps10 locus-specific protocol is to amplify the oomycete rps10 locus for metagenomic research.


## Ordering rps10 locus-specific primers

Rps10 oligos were designed by Frank Martin and Val Fieland and are listed here in the 5' -> 3' orientation
Both the rps10 forward and reverse primer binding sites have SNPs.
To reduce the amount of primer degeneracy in the rps10 locus-specific PCR reaction it is advisable to order multiple specific oligo sequences for the reverse primer sequences rather than ordering oligos with IUPAC ambiguity codes.
Using the IUPAC code Y (C,T) for the rps10_F_Conserved oligo is optional but simplifies the primer mixture step. 

## Rps10 locus-specific forward primers

* before space = Forward 5' Illumina overhang adapter sequence
* after space  = Rps10 locus-specific forward primer

```{r}
custom_kable(tibble(
  "Primer name" = c("rps10_F_Conserved", "rps10_F2_Conserved"),
  "Forward Primer sequence" = c("TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG GTTGGTTAGAGYAAAAGACT",
                                "TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG GTTGGTTAGAGTAGAAGACT")
))
```


## Rps10 locus-specific reverse primers

* before space = Reverse 5' Illumina overhang adapter sequence)
* after space  = Rps10 locus-specific reverse primer

```{r}
custom_kable(tibble(
  "Primer name" = paste0("rps10_R", 1:7),
  "Forward Primer sequence" = c("GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATGCTTAGAAAGATTTGAACT",
                                "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATACTTAGAAAGATTTGAACT",
                                "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATGCTTAGAAAGACTTGAACT",
                                "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATGCTTAGAAAGACTCGAACT",
                                "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATGCCTAGAAAGACTCGAACT",
                                "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATGTTTAGAAAGATTCGAACT",
                                "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATGCTTAGAAAGATTCGAACT")
))
```


## Rps10 locus-specific primer mixture

```{r}
custom_kable(read_tsv("tables/metabarcoding_primer_mixing.tsv"))
```

Notes:

* We ordered the Rps10 locus-specific oligos from Life technologies, but other sources will probably work just as well.
* The TE Buffer (Tris-EDTA) is a 1X Solution, pH 8.0, Molecular Biology Grade (Cat. No. BP2473100 )
* The two primers represented by rps10_F_Conserved each have a final concentration of 2.0µM


