---
title: "Rps10 metabarcoding primer ordering and mixing protocol"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
geometry: left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm
---

```{r setup, include=FALSE}
source("style.R")
```

*Updated October 2018*

This protocol is used to prepare PCR primers for the rps10 locus for metabarcoding.


## Ordering rps10 locus-specific primers

Both the rps10 forward and reverse primer binding sites have SNPs.
To reduce the amount of primer degeneracy in the rps10 locus-specific PCR reaction it is advisable to order multiple specific oligo sequences for the reverse primer sequences rather than ordering oligos with IUPAC ambiguity codes.
Using the IUPAC code Y (C,T) for the rps10_F_Conserved oligo is optional but simplifies the primer mixture step. 


## Rps10 locus-specific forward primers

```{r}
custom_kable(tibble(
  "Primer name" = c("rps10\\_F\\_Conserved", "rps10\\_F2\\_Conserved"),
  "Forward Primer sequence (5' -> 3')" = c(paste0("TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG", footnote_marker_number(1), " GTTGGTTAGAGYAAAAGACT", footnote_marker_number(2)),
                                           "TCGTCGGCAGCGTCAGATGTGTATAAGAGACAG GTTGGTTAGAGTAGAAGACT")
)) %>% footnote(number = c("before space = Forward 5' Illumina overhang adapter sequence",
                           "after space  = Rps10 locus-specific forward primer"))
```


## Rps10 locus-specific reverse primers

```{r}
custom_kable(tibble(
  "Primer name" = paste0("rps10\\_R", 1:7),
  "Reverse Primer sequence  (5' -> 3')" = c(paste0("GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG", footnote_marker_number(1), "ATGCTTAGAAAGATTTGAACT", footnote_marker_number(2)),
                                            "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATACTTAGAAAGATTTGAACT",
                                            "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATGCTTAGAAAGACTTGAACT",
                                            "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATGCTTAGAAAGACTCGAACT",
                                            "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATGCCTAGAAAGACTCGAACT",
                                            "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATGTTTAGAAAGATTCGAACT",
                                            "GTCTCGTGGGCTCGGAGATGTGTATAAGAGACAG ATGCTTAGAAAGATTCGAACT")
)) %>% footnote(number = c("before space = Reverse 5' Illumina overhang adapter sequence",
                           "after space  = Rps10 locus-specific reverse primer"))
```


## Rps10 locus-specific primer mixture

```{r}
data <- read_tsv("tables/metabarcoding_primer_mixing.tsv")
data$Reagent <- gsub(data$Reagent, pattern = "_", replacement = "\\_", fixed = TRUE)
data[1, 3] <- paste0(unlist(data[1, 3]), footnote_marker_number(2))
data[10, 1] <- paste0(unlist(data[10, 1]), footnote_marker_number(3))
custom_kable(data) %>% 
  footnote(number = c("We ordered the Rps10 locus-specific oligos from Life technologies",
                      "The two primers represented by rps10_F_Conserved each have a final concentration of 2.0µM",
                      "The TE Buffer (Tris-EDTA) is a 1X Solution, pH 8.0, Molecular Biology Grade (Cat. No. BP2473100)"))
```



